---
title: 'Introduction to the tvReg package'
author:
- name: Isabel Casas
  affiliation: University of Deusto
- name: Ruben Fernandez-Casal
  affiliation: University of A Coruna
date: '`r paste("tvReg", packageVersion("tvReg"))`'
output: 
  rmarkdown::html_vignette:
    toc: yes
    toc_depth: 2
  html_document:
    toc: yes
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{Introduction to the tvReg package} 
  %\VignetteEngine{knitr::rmarkdown} 
  %\usepackage[UTF-8]{inputenc}
---

<!-- 
abstract: "The source code of the *tvReg* package is publicly available
for download from the Comprehensive *R* Archive Network (CRAN,
https://CRAN.R-project.org/). "

Pendiente:
- Actualizar funciones `tvLM()`
-->


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 6,
                      fig.height = 4, fig.align = "center")
library(tvReg)
```

The five basic functions in this package are *tvLM*, *tvAR*, *tvSURE*, *tvPLM*, *tvVAR*  and *tvIRF*. Moreover, this package provides the *confint*, *fitted*, *forecast*, *plot*, *predict*, *print*, *resid* and *summary* methods adapted to the class attributes of the *tvReg*. In addition, it includes a bandwidth selection method, a time-varying variance-covariance estimator and two estimation procedures: the time-varying ordinary least squares, which is implemented in the *tvOLS* method and the time-varying generalised least squares, which is implemented in the *tvGLS* method.

# Single equation models: the TVLM and TVAR 

The general formula of these models is:
$$
y_t = X_t' \beta_t + u_t,  \hspace{0.3cm} t = 1, \ldots, T  \ \ \ (1)
$$
where $X_t = (X_{0t}, X_{1t}, \ldots, X_{dt})'$ and $\beta_t = (\beta_{0t}, \beta_{1t}, \ldots, \beta_{dt})'$ are vectors and $u_t$ is a random variable. When $X_t$ contains lags of $y_t$ then we have the time-varying coefficients AR model (TVAR) which is fitted by function *tvAR*. When $X_t$ contains only exogenous variables, then the model is denoted by TVLM and it is fitted by function *tvLM*.


## Standard usage of *tvLM*

Function *tvLM* fits a TVLM to the data using the *tvOLS* method in the estimation. The only mandatory argument is *formula* which should be a single formula for a single equation model. This formula follows the standard regression formula in *R* (see documentation of *formula*). An object of the class attribute *tvlm* is returned. 

The following example demonstrates the functionality of *tvLM* on generated data and compares it with the *lm* estimation. The latter assumes that the model coefficients are constant. The data generating process of the example below has time-varying coefficients and therefore its estimation with function *lm* will only find a central value of the time-varying coefficients.

We want to estimate the following model:
$$
y_t  = \beta_{1t} X_{1t}+ \beta_{2t} X_{2t} + u_t, \ \ t = 1, \ldots, T,
$$
where the coefficients are functions of a rescaled time period $\tau = t/T$ with $T = 1000$. In particular, $\beta_{1t}= \sin(2\pi\tau)$ and $\beta_{2t} = 2\tau$. The regressors, $X_{1t} \sim N(0, 1)$ and $X_{2t} \sim \chi^2_4$, are independent of the error term, $u_t \sim t_{10}$. 


```{r tvLM}
 ##Simulate a linear process with time-varying coefficient
 ##as functions of rescaled time period.
 library(tvReg)
 tau <- seq(1:1000)/1000
 beta <- data.frame(beta1 = sin(2 * pi * tau), beta2 = 2 * tau)
 X1 <- rnorm(1000)
 X2 <- rchisq(1000, df = 4)
 error <- rt(1000, df = 10)
 y <- apply(cbind(X1, X2) * beta, 1, sum) + error
 data <-data.frame(y = y, X1 = X1, X2 = X2)

 ##Estimate coefficients with lm and tvLM for comparison
 coef.lm <- stats::lm(y ~ 0 + X1 + X2, data = data)$coef
 model.tvLM <- tvLM(y ~ 0 + X1 + X2, data = data)

 ##Plot the estimates of beta1
 par (mar = c(4,4,1,1), oma = c(1,1,1,1))
 plot(tau,beta[, 1], type = "l", main = "", ylab = expression(beta[1]),
 xlab = expression(tau), ylim = range(beta[,1], model.tvLM$coefficients[, 1]))
 abline(h = coef.lm[1], col = 2)
 lines(tau, model.tvLM$coefficients[, 1], col=4)
 legend("topright", c(expression(beta[1]), "lm", "tvlm"), col = c(1, 2, 4), 
        bty = "n", lty = 1, cex = 0.8)
```

The first line loads the *tvReg* package. Then data is simulated and a data frame is created with the dependent variable and the regressors. Estimations of this model are obtained with the *lm* and the *tvLM* functions for comparison. As we see in the plot, the estimation assuming a constant $\beta_{1t}$ lays in the middle of all the values of $\beta_{1t}$, while the estimation assuming time-varying coefficients is more accurate and closer to the true values.

Package *tvReg* calculates the confidence intervals the class attributes *tvlm*, *tvar*, *tvsure* and *tvirf* with the *confint* method. The argument *level* is set to 0.95 (95% confidence interval) by default. If this argument is chosen to be a number between 0 and 1, then a number of *runs* resamples is used in the confidence interval calculation. Because coefficients are time-varying, only wild bootstrap residual resampling is possible. Two choices of wildbootstrap are available in argument *tboot*, the Mammen (1993) (default) and the one using the normal distribution (tboot ="wild2"). 

Note that the input model in the *confint* method has already confidence intervals, the calculation of another confidence interval will be faster as the results from replications are stored in variable *BOOT*. Below the code to calculate the 90% and 95% coefficient confidence intervals for the *model.tvLM*.

```{r CI, eval = TRUE}

##Obtain the 90% confidence interval of the coefficients for an object of the class attribute tvlm
model.tvLM.90 <- confint (model.tvLM, level = 0.90, runs = 50)

##Obtain the 95% confidence interval of the same object. This will reused the resamples of object model.tvLM.90. So the second confidence interval calculation is faster
model.tvLM.95 <- confint(model.tvLM.90)
```

There is a plot method for objects of the five class attributes in this package. The variable coefficients estimates, as well as if confidence intervals if calculated, are plotted for the class attributes *tvlm*, *tvar*, *tvsure* and *tvirf*. The fitted values and the residuals are plotted for the class attribute *tvvar* because the interpretation of its coefficients is not relevant. Below the *plot* of *model.tvLM.90*.


```{r PLOT,  eval = TRUE}
##Plot coefficient estimates and confidence intervals (if calculated) of objects of the class attribute tvlm
plot(model.tvLM.90)
```

## User options of *tvLM*
The user can provide additional optional arguments to modify the default estimation. All optional arguments are described below:


### Smoothing random variable

*tvLM* assumes by default that model coefficients are unknown functions of rescaled time, $\tau = t/T$ and therefore argument *z* is set to *NULL* by default. The user can modify this setting by entering a numeric vector in argument *z* with the values of the random smoothing variable over the corresponding time period. The example below shows this functionality with generated data. The example generating process of function *arima.sim* from package *stats* is used in the example.

```{r tvLM2}
 ##Data generation
 set.seed (42)
 z <- stats::arima.sim (n = 1000, list(ar = c(0.8897, -0.4858), ma = c(-0.2279, 0.2488)), sd = sqrt(0.1796))
 beta <- data.frame(beta1 = sin(2 * pi * z), beta2 = 2 * z)
 y <- apply(cbind(X1, X2) * beta, 1, sum) + error
 data<-data.frame(y = y, X1 = X1, X2 = X2, z = z)
 
 ##Coefficients estimation
 coef.lm <- stats::lm(y ~ 0 + X1 + X2, data = data)$coef
 model.tvLM2 <- tvLM(y ~ 0 + X1 + X2, z = z, data = data, cv.block = 50, est = "ll")
 
 ##Plotting the estimates of beta1
 sort.index <- sort.int(z, index.return = TRUE)$ix
 par (mar = c(4,4,1,1), oma = c(1,1,1,1))
 plot(z[sort.index], beta[sort.index, 1], type = "l", main = "",
 ylab = expression(beta[1]), xlab = expression(z[t]),
 ylim = range(beta[,1], coefficients(model.tvLM2)[, 1]))
 abline(h = coef.lm[1], col = 2)
 lines(z[sort.index], model.tvLM2$coefficients[sort.index, 1], col = 4)
 legend("top", c(expression(beta[1]), "lm", "tvLM"), col = c(1, 2, 4), bty = "n", 
        lty = 1, cex = 0.5)
```


As expected, the coefficient estimate from *lm* falls around the mean of all $\beta_{1t}$. While the *tvLM* estimates follow the true process closely. Note that if the bandwidth was very large, then the two estimates would be very similar.

### Data
Argument *data* can be used to specify the data frame or matrix with the model variables. If it is not specified, the function searches variables in the global environment or the one attached to the search path.


### Bandwidth
When argument *bw* is  set to *NULL* in *tvLM*, it is automatically selected by leave-(2l+1)-out cross-validation. The default is leave-one-out cross-validation, i.e $l=0$ but his values can be changed by entering a value different than zero in argument  *cv.block*. This data-driven bandwdith selection can be a bit slow for large datasets, and it should be avoided if the user knows the value of the bandwidth for the required problem. The user can enter values in *bw* to obtain undersmoothed or oversmoothed estimates as needed. As we can see in the previous example, the bandwidth was chosen to 0.4 by the user.

### Kernel type
The two choices for this argument are *tkernel = "Epa"* (default) and   *tkernel ="Gaussian"*. The former refers to the Epanechnikov kernel, which is compact in [-1, 1]. The  authors do not recommend the use of the Gaussian kernel because in general, it requires more calculations and it is slower.

### Estimation methodology
The default estimation methodology is the Nadaraya-Watson or local constant, which is set as  (*est = "lc"*) and it fits a constant at each interval defined by the bandwidth. The argument *est = "ll"* can be chosen to perform a local linear estimation (i.e., to fit a polynomial of order 1).


### Singular fit
As the *tvOLS* method wraps the *lm.wfit* method, which at default allows the fitting of a low-rank model, and the estimation coefficients can be *NA*s. The user can change argument *singular.ok* to *FALSE*, so the program stops in case of a low-rank model.


## Standard usage of *tvAR*

A TVAR model is a special case of TVLM in which regressors contain lagged variables of the dependent variable, *y*. The number of lags included depend on the model order *p*. Other exogenous variables may be included in the model using argument *exogen*. An intercept is included by default unless the user enters *type= "none"* into the function call. Econometrically, this function also wraps estimator *tvOLS* which needs a bandwidth *bw* that is automatically selected by cross-validation when the user does not enter any number. An object of the class attribute *tvar* is returned.

The following examples demonstrates the functionality of *tvAR* on generated data, and compares it with the output of the *ar.ols* method from the *stats* package. Specifically, the following TVAR(2) process is considered,

$$
y_t  = \beta_{1t} y_{t-1}+ \beta_{2t} y_{t-2} + u_t, \ \ t = 1, \ldots, T,
$$
with coefficients $\beta_{1t} = 0.5 \cos(2\pi \tau)$ and $\beta_{2t} = (\tau -0.5)^2$, where $\tau = t/T$, and standard normal errors. A random proces of 1000 points is generated, but only the last 500 are used in the estimation to remove the dependency on the initial values.

```{r tvAR}
 ##Simulate an tvAR(2) process
 tt<-(1:1000)/1000
 beta <- cbind( 0.5 * cos (2 * pi * tt), (tt - 0.5)^2)
 y<-numeric(1000)
 y[1] <- 0.5
 y[2] <- -0.2
 ##y(t) = beta1(t) y(t-1) + beta2(t) y(t-2) + ut
 for (t in 3:1000)
 {
   y[t] <- y[(t-1):(t-2)] %*% beta[t,] + rnorm(1)
 }
 Y <- tail (y, 500)
 
 ##Coefficient estimates of process Y with ar.ols and tvAR
 model.ar.2p <- ar.ols(Y, aic = FALSE, order = 2, intercept = FALSE, demean = FALSE)
 model.tvAR.2p <- tvAR(Y, p = 2, type = "none", est = "ll")
```

The smoothing variable in the chunk above is time. The lines of code below show an example of a TVAR(1) process whose coefficient is a function of a uniform random variable in [-1, 1]. In particular, $\beta_{1t} = (z_t -0.5)^2$. It also calculates the coefficient 80% confidence interval and plot the estimates.

```{r tvAR.z}
##Simulate a AR(1) process with coefficients depending on z
z <- runif(2000, -1, 1)
beta <- (z - 0.5)^2
y <- numeric(2000)
y[1] <- 0.5
error <- rnorm(2000)
 ##y(t) = beta1(z(t)) y(t-1) +  ut
for (t in 2:2000)
{
 y[t] <- y[(t-1)] %*% beta[t] + error[t]
}

##Remove initial conditions effects
Z <- tail (z, 1500)
Y <- tail (y, 1500)

##Coefficient estimates of process Y with ar.ols and tvAR
model.ar.1p <- ar.ols(Y, aic = FALSE, order = 1, intercept = FALSE, demean = FALSE)
model.tvAR.1p.z <- tvAR(Y, p = 1, z = Z, type = "none", est = "ll")

##80% confidence interval using normal wild bootstrap for object of the class attribute tvar with 200 bootstrap resamples 
model.tvAR.80 <- confint(model.tvAR.1p.z, tboot = "wild2", level = 0.8, runs = 50)

##Plot coefficient estimates of objects of the class attribute tvar.
plot(model.tvAR.80)

```


The *print* method only displays the mean of the coeffient estimates over time and the mean of their confidence interval, if calculated. The *summary* method displays a summary of all coefficient values over the whole time period. It also prints a pseudo-R2 for the class attributes *tvlm*, *tvar*, *tvsure* and *tvvar*. See how it works below.

```{r  PRINT, eval = TRUE}
##Summary of model.tvAR.80
summary(model.tvAR.80)

##Print of model.tvAR.80
print(model.tvAR.80)
```

## User options of *tvAR*
The user can provide additional optional arguments to modify the default estimation. See section 'User options of *tvLM*' to understand the usage of arguments *bw*, *est*, *tkernel* and *singular.ok*. In addition, the *tvAR* has the following arguments:

### Type
The default model contains an intercept (i.e., it has a mean different from zero). The user can set argument *type = "none"*, so the model has mean zero.


### Autoregressive model with coefficent restrictions
An autoregressive process of order *p* does not necessarily contain all the previous p-lags of $y_t$. Argument *fixed*, with the same format as in the function *arima* from the package *stats*, permits to impose these restrictions. The order of variables in the model is: intercept (if any), lag 1, lag 2, $\ldots$, lag p and exogenous variable (if any). By default, the argument *fixed* is a vector of *NA*s with length the number of coefficients in the model. The user can enter a vector in the argument *fixed* with zeros in the positions corresponding to the restricted coefficients.

The example below uses the simulated variable *Y* from above and fits a TVAR(6), but only the first, third and sixth lags are considered in the model, the model has an intercept and there are no exogenous variables. 

```{r tvAR2, eval = FALSE}
 ##Estimate only coefficient from odd lags and the intercept
 tvAR.6p <- tvAR(y, p = 6, type = "const", fixed = c(NA, NA, 0, NA, 0, NA, 0), est = "ll")
```


# Multi-equation linear models

The formula of systems of linear models can be generally express as in (1) with $y_t = (y_{1t}, y_{2t}, \ldots, y_{Mt})'$ for $M$ the number of equations in the system. Similarly, the error term $u_t =(u_{1t}, u_{2t}, \ldots, u_{Mt})'$ and the $\Sigma_t$ is the variance-covariance matrix that defines the dependency of the error terms of all equations. Variables $X_t$ and $\beta_t$ are matrices. 

Regarding systems of equations, the *tvSURE* function fits a time-varying seemingly unrelated equations models. Its main argument is *formula* which is a list of objects of the class attribute *formula*, one formula for each equation. Equations may have a different number of regressors and these do not have to be the same. 

Another multi-equation model included in the package is the time-varying vector autoregressive in function *tvVAR* whose main arguments are a matrix of dependent variables *y* and the number of lags *p*. It returns an object of the class attribute *tvvar*. Coefficients of the *tvVAR* are not interpretable, instead the time-varying coefficients impulse response function is coded in function *tvIRF*. The latter takes an object of the class attribute *tvvar* and returns an object of the class attribute *tvirf*. 


## Standard usage of the tvSURE

A time-varying coefficients SURE model is a multi-equation where the regressors are exogenous variables. The main argument of this function is a list of formulas, one for each equation. The *formula* format is inpired in the formula from package *systemfit* which estimates parametric multi-equation problems with constant coefficients. An object of the class attribute *tvsure* is returned by the main function *tvSURE*.


The examples below use the dataset *Kmenta* from package *systemfit* to illustrate a demand/supply problem using different models. This problem has two equations: i) a demand equation, which explains how food consumption per capita, *consump*, depends on the ratio of food price, *price*; and disposable income, *income*; and ii) a supply equation, which shows how consumption depends on *price*, ratio prices received by farmers to general consumer prices, *farmPrice*; and  a possible time trend, *trend*. Mathematically, this SURE model is

\begin{align}
consump_t = &\beta_{10} + \beta_{11} price_t + \beta_{12} income_t  + u_{1t}\nonumber\\
consump_t = &\beta_{20} + \beta_{21} price_t+ \beta_{22} farmPrice_t  +\beta_{23} t+  u_{2t}.
\label{eq:Kmenta}
\end{align}


The estimation of this multi-equation problem can be done equation by equation, assuming no correlation in the error variance-covariance matrix, or as a system where the information in this matrix is used. Regressors can be different for each equation. An intercept is included by default in each equation unless its *formula* states it differently. Function *tvSURE* is a wrapper of the two estimation procedures. Estimator *tvOLS* is used by default, calculating estimates for each equation independently with different bandwidths *bw*. The user is able to enter a set of bandwidths or a single bandwidth to be used in the estimation instead. In addition, estimator *tvGLS* is used when equations are assumed to be related by the variance-covariance matrix of the error. In addition, confidence intervals of the estimates can be calculated. Results can be plotted and summarise.

```{r tvOLS}
data("Kmenta", package = "systemfit")
eqDemand <- consump ~ price + income
eqSupply <- consump ~ price + farmPrice + trend
system <- list(demand = eqDemand, supply = eqSupply)

##OLS estimation of a system
model.ols <- systemfit::systemfit(system, method = "OLS", data = Kmenta)

##tvOLS estimation of a system with the local linear estimator
model.tvOLS <- tvSURE(system, data = Kmenta,  est = "ll")

##50% confidence interval using Mammen's wild bootstrap for object of the class attribute tvsure
model.tvOLS <- confint(model.tvOLS, level = 0.5, runs = 30)

##Plot coefficient estimates and confidence intervals (if calculated) of objects of the class attribute tvsure
plot(model.tvOLS)

##Print of model model.tvOLS 
print(model.tvOLS)
```

## User options of *tvSURE*
The user can provide additional optional arguments to modify the default estimation. Refer to section 'User options of *tvLM*' to understand the usage of arguments *z*, *data*, *bw*, *est*, *tkernel* and *singular.ok*. Note that the current version only allows one single random variable *z* for all equations. The *tvSURE* function wraps estimators *tvOLS* and *tvGLS*. 

### Choosing the estimation method 
This argument defines the type of estimation to be performed. The possible choices in argument *method* are:

1. "tvOLS" for a line by line estimation, meaning that the error variance-covariance matrix, $\Sigma$, is the identity matrix.

2. "tvGLS" to estimate the coefficients of the system using $\Sigma_t$, for which the user must enter it in argument *Sigma*. Argument *Sigma* takes either a symmetric *matrix* or an *array*. If $\Sigma$ is a *matrix* (constant over time), then it must have dimensions *neq* $\times$ *neq*, where *neq* is the number of equations in the system. If $\Sigma_t$ is considered to change with time, then argument *Sigma* is an *array* of dimension *neq* $\times$ *neq* $\times$ *obs*, where the last dimension measures the number of time observations. Note that if the user enters a diagonal variance-covariance matrix with diagonal values different from one, then a time-varying weighted least squares is performed. If *method = "tvGLS"* is entered but *Sigma = NULL*, then *tvSURE* is fitted as if \code{method = "tvOLS"} and a warning is issued.

3. "tvFGLS" to estimate the coefficients of the system using an estimated time-varying variance-covariance matrix. By default, only one iteration is performed in the estimation of $\Sigma$, unless *control* indicates otherwise. The user can choose the maximum number of iterations or the level of tolerance in the estimation of $\Sigma$. 


The lines of code below illustrate the use of arguments *method* and *control* and compares it with the usage of these arguments in function *systemfit*.

```{r tvFGLS}
##FGLS estimation - SURE estimation
fgls1.fit <- systemfit::systemfit(system, data = Kmenta, method = "SUR")

##tvFGLS estimation - tvSURE estimation
tvfgls1.fit <- tvSURE(system, data = Kmenta, method = "tvFGLS")
```

```{r tvFGLS2}
##Iterative FGLS estimation - SUR estimation
fgls2.fit <- systemfit::systemfit(system, data = Kmenta, method = "SUR", maxit = 100)

##Iterative tvFGLS estimation - SURE estimation using the local linear
tvfgls2.fit <- tvSURE(system, data = Kmenta, method = "tvFGLS",
control = list(tol = 0.001, maxiter = 100))
```

### Coefficient restrictions

The user can restrict certain coefficients using arguments *R* and *r*. Note that the restriction is setting those coefficients to a constant. Restrictions can aid statistical inference to test certain conditions.  Matrix *R* has as many rows as restrictions in *r* and as many columns as regressors in the model. In this case, Model (\ref{eq:Kmenta}) has 7 coefficients which are ordered as they appear in the list of formulas. Note that the time-varying coefficient of the variable *trend* is redundant when an intercept is included in the second equation of the TVSURE. Therefore, we want to restrict its coefficient two zero. We would also like to impose $\beta_{11, t} - \beta_{21, t} = 0.5$:

$$
\left(\begin{array}{ccccccc}
0 &0& 0&0&0&0&1\\
0&1&0&0&1&0&0 \end{array}\right)  \left(\begin{array}{c} \beta_{10, t} \\ \beta_{11,t} \\\beta_{12, t}\\\beta_{20,t} \\\beta_{21, t} \\\beta_{22,t} \\ \beta_{23, t} \\ \end{array}\right) =  \left(\begin{array}{c} 0 \\0.5 \end{array}\right) 
$$

This is done with the \code{tvSURE} as follows:


```{r tvFGLS.rest,  eval = FALSE}
##Estimation with 2 restrictions
Rrestr <- matrix(0, 2, 7)
Rrestr[1, 7] <- 1
Rrestr[2, 2] <- 1
Rrestr[2, 5] <- -1
qrestr <- c(0, 0.5)
tvfgls.rest <- tvSURE(system, data = Kmenta, method = "tvFGLS",
R = Rrestr, r = qrestr, bw = tvfgls1.fit$bw, bw.cov = tvfgls1.fit$bw.cov)
```


## Standard usage of *tvPLM*
The *tvPLM* method is inspired by the  *plm* from the package *plm*. It converts *data* into an object of the class attribute *pdata.frame* using argument *index* to define the cross-section and time dimensions. If *index = NULL* (default), the two first columns of *data* define the two dimensions.

The *tvPLM* wraps the *tvRE* and *tvFE* methods to estimate the coefficients of time-varying panel data models.

## User options of *tvPLM*
The user can provide additional optional arguments to modify the default estimation. See section ``Standard usage of *tvLM*" for details on arguments *z*, *data*, *bw*, *est* and *tkernel*. Note that the current version only allows one single smoothing random variable, *z*, for all equations. Furthermore, argument *method* defines the estimator used. The possible choices are: "pooling" (default), "random" and "within".

##  Application to health policy

The income elasticity of healthcare expenditure is defined as the percentage change in healthcare expenditure in response to the percentage change in income per capita. If this elasticity is greater than one, then healthcare expenditure grows faster than income, as luxury goods do, and is driven by market forces alone. The heterogeneity of health systems among countries and time periods have motivated the use panel data models for example in Gerdtham et al (1992) who use a fixed effects (FE) model. In addition to the income per capita, measured by the log GDP, the literature has identify the ratio of population over 65 years old, population uner 15 years old and the ratio of public funding of healcare as important variables in this problem. The income elasticity estimate with a FE developed in thepackate *plm* is greater than 1, a counter-intuitive result. This issue is resolved using the TVFE developed in the \pkg{tvReg}. Find the code below:

```{r tvPLM,  eval = TRUE}
data("OECD")
print(names(OECD))
elast.fe <- plm::plm(lhe ~ lgdp + pop65 + pop14 + public, data = OECD, 
                     index = c("country", "year"), model = "within")
elast.tvfe <- tvPLM (lhe ~ lgdp + pop65 + pop14 + public, data = OECD, 
                     index = c("country", "year"), method = "within", bw = 0.6)
elast.fe <- confint(elast.fe)
elast.tvfe <- confint(elast.tvfe)
plot(elast.tvfe, vars = 1, ylim = c(0.45, 1.3))
graphics::par(mfrow = c(1, 1), 
                mar = c(4, 4, 2, 1), oma = c(0, 0, 0, 0))
x.axis <- 1:elast.tvfe$obs
par(new = TRUE)
plot(x.axis, rep(mean(elast.fe[1,]), elast.tvfe$obs), ylim = c(0.45, 1.3),
     ylab ="", xlab ="", type = "l")
graphics::polygon(c(rev(x.axis), x.axis), 
                  c(rep(rev(elast.fe[1, 2]), elast.tvfe$obs),
                    rep(elast.fe[1, 1], elast.tvfe$obs)),
                  col = "grey10", border = NA, fillOddEven = TRUE)
lines(x.axis, rep(mean(elast.fe[1,]), elast.tvfe$obs), col ="white")
```

## Standard usage of *tvVAR* and *tvIRF*

A time-varying coefficients vector autoregressive (TVVAR) model is a system of TVAR models. The dependent variable, *y*, is a matrix with as many columns as equations. Regressors are often the same for each equation and they consist of the lagged values of *y*, where the number of lags is given in argument *p*; an intercept if argument *type="const"* and other exogenous variables entered in argument *exogen*. Econometrically, the *tvOLS* is called to calculate the estimates for each equation independently using one bandwidth per equation. The user can enter a single scalar in *bw* or a vector of scalars, one bandwidth for each equation. If *bw = NULL*, one bandwidth for each equation is selected by cross-validation. 

As in the other models, the kernel and the estimation methodology can be chosen in arguments *tkernel* and *est*. The return is an object of the class attribute *tvvar* which can be used to estimate the time-varying impulse response function with function *tvIRF*. The smoothing variable is time by default, but another random variable can be used by entering it in argument *z*.

Example below uses the macroeconomic data from Primiceri (2005). Three variables are included in dataset *usmacro* from package *bvarsv*: inflation rate (*inf*), unemployment rate (*une*) and treasury bill interest rate (*tbi*) for the United States. The mathematical model under study follows the expression of a TVVAR(4):

$$
\text{inf}_t = a_{t}^1 +\sum_{i=1}^4 b_{it}^ 1 \ \text{inf}_{t-i} +\sum_{i=1}^4 c_{it}^1 \ \text{une}_{t-i} +\sum_{i=1}^4 d_{it}^1\ \text{tbi}_{t-i} +u _{t}^1
$$

$$
\text{une}_t = a_{t}^2 +\sum_{i=1}^4 b_{it}^ 2 \ \text{inf}_{t-i} +\sum_{i=1}^4 c_{it}^2 \ \text{une}_{t-i} +\sum_{i=1}^4 d_{it}^2 \ \text{tbi}_{t-i} +u _{t}^2
$$

$$
\text{tbi}_t = a_{t}^3 +\sum_{i=1}^4 b_{it}^ 3 \ \text{inf}_{t-i} +\sum_{i=1}^4 c_{it}^3 \ \text{une}_{t-i} +\sum_{i=1}^4 d_{it}^3\ \text{tbi}_{t-i} +u _{t}^3.
$$

A constant coefficients VAR(4) is estimated using function *VAR* from package *vars* and a TVVAR(4) is estimated with *tvVAR*.

```{r tvVAR}
##Inflation rate, unemployment rate and treasury bill interest rate for the US,
##as used by Primiceri (2005).
data(usmacro, package = "bvarsv")
model.VAR <- vars::VAR(usmacro, p = 4, type = "const")
model.tvVAR <- tvVAR(usmacro, p = 4, type = "const")

##Plot the fitted values and residuals of each equation in the model 
plot(model.tvVAR)
 
```

The user can provide additional optional arguments to modify the default estimation. Refer to section 'User options of *tvAR*' to understand the usage of arguments *p*, *z*, *bw*, *type*, *exogen*, *est*, *tkernel* and *singular.ok*. Note that the current version only allows one single random variable *z*, the same for every equation. The *tvVAR* model wraps estimator *tvOLS*. At the moment all equations are estimated as if there were independent, i.e. line by line. The variance-covariance matrix in the residuals can be used to calculate the orthogonal time-varying IRF.

## User options of *tvIRF*
The main argument *x* is an object of the class attribute *tvvar* obtained from function *tvVAR*. The user can provide additional optional arguments to modify the default estimation. 

### Impulse and response variables
The user has the option to pick a subset of impulse variables and/or response variables using arguments *impulse* and *response*.

### Horizon
The horizon of the TVIRF coefficients can be chosen by the user with argument *n.ahead*, the default is 10.

### Orthogonal TVIRF
The *tvIRF* calculates one impulse response function for each point in time. It is likely that the errors variance-covariance matrix of a process with time-varying coefficients is also time-varying. Those, the default of
argument *ortho.cov = "tv"*. Note that the user can enter a value of the bandwidth for the covariance matrix estimation in *bw.cov*. This function calls function *tvCov* in the calculation of the MA ($\infty$) coefficients. It is possible to use a constant variance-covariance matrix by setting *ortho.cov = "const"*.

The chunk below shows how to obtain the IRF and TVIRF from the previous monetary policy example.

```{r tvIRF}
##Estimate a the impulse response functions with irf and tvIRF from 
##previous vector autoregressive models
model.irf <- vars::irf(model.VAR)
model.tvIRF <- tvIRF(model.tvVAR)

##95% confidence interval using Mammen's wild bootstrap for object of the class attribute tvirf
model.tvIRF <- confint(model.tvIRF, runs = 30)
```

Note that there is one IRF for each point in time. The *plot* method of class attribute *tvirf* displays the mean value of all the IRF over all the time period. However, if the user desires to plot the TVIRF of a particular time, for example value 100 as below, then it is entered in the argument *obs.index*. This *plot* method also permits to choose a particular response and impulse variables.

```{r tvIRF2}
##Plot the mean all tvIRF over time
plot(model.tvIRF)

##Plot the effect of a shock in the interest rates (tbi) on the inflation (inf)
##at time 100
plot(model.tvIRF, obs.index = 100, impulse = "tbi", response = "inf")
```


### Cumulative TVIRF
If the user desires to obtain the cumulative TVIRF values, then argument  *cumulative* must be set to *TRUE*. See example below.

```{r tvIRF3}
##Estimate a the tvIRF with time-varying covariance function
model.tvIRF2 <- tvIRF(model.tvVAR, cumulative = TRUE)

##Plot the cumulative effect on a shock in short term interest rates (tbi) 
##on the inflation (inf)
plot <- plot(model.tvIRF2, impulse ="tbi", response = "inf")


```


# Estimating a time-varying variance-covariance matrix

A time-varying covariance matrix of two or more series can be estimated using function *tvCov* as in the example below. This is the function used by the *tvSURE* and *tvIRF* functions to estimate a time-varying variance-covariance matrix of the error term. The lines of code below illustrate its use.

```{r Sigma}
library(MASS)
##Generate two independent (uncorrelated) series
y<-cbind(rnorm(200, sd= 4), rnorm(200, sd=1))
##Calculate the bandwidth
bw.cov<-bwCov(y)
##Estimate variance-variance matrix
Sigma.hat<- tvCov(y, bw=bw.cov)
##The first time point estimate
print(Sigma.hat[,,1])
##The mean over time of all estimates
print(apply(Sigma.hat, 1:2, mean))

##Generate two dependent variables with a covariance of -0.5
y <- mvrnorm(n = 200, mu = c(0,0), Sigma = cbind(c(1, -0.5), c(-0.5, 4)))
##Calculate the bandwidth
bw.cov <- bwCov(y)
##Estimation the variables variance-covariance matrix
Sigma.hat <- tvCov(y, bw = bw.cov)
##The first time point estimate
print(Sigma.hat[, , 1])
```




# Prediction and forecast in time-varying coefficient models

Estimation is an useful tool to understand the patterns and processes hidden in known data. Prediction and forecasting are the mechanisms to extend this understanding to unknown data. 

In a classical linear model, the *prediction* of the dependent variable at time $T+h$ is $\hat y_{T+h} = x_{T+h}^\top \hat \beta$ for $h\ge 1$. All predictors, $x_{T+h}$, are known. 

In autoregressive models, the prediction of future values has a slightly different nature and it is commonly referred to as *forecast*. The predictors (regressors) in the 1-step-ahead forecast are known, but they are unknown for longer horizons. For example, given $y_t = 5 - 0.5 y_{t-1} + u_t$ for $t = 1, \ldots, T$, the 1-step-ahead forecast is $\hat y_{T+1} = 5 -0.5 y_{T}$ with known $y_T$. However, the 2-step-ahead forecast is $\hat y_{T+2} = 5 - 0.5 \hat y_{T+1}$ with the previously forecasted $\hat y_{T+1}$ as predictor, which means a larger uncertainty in the forecast error. This means a greater uncertainty in the forecast error as the forecast horizon increases.

In our the time-varying coefficient models, we refer to prediction when the smoothing variable, $z_t$, is a random variable and to forecast when $z_t = \tau$. Thus, the *predict* and *forecast* methods in *tvReg* are slightly different. 


## Usage of prediction and forecast in tvReg

The *forecast* method is implemented for the class attributes *tvlm*, *tvar*, *tvvar* and *tvsure*. As an example, the three days ahead forecast of model *tvHAR*, which is an extension of the HAR model of Corsi (2008) to allow for time-varying coefficients. This is a TVAR(1) model with two exogenous variables: an average of a weekly realized variance and an average of a monthly week variance. The argument *newexogen* needs three values for time points 2002, 2003 and 2004 and variable *n.ahead* is set to three. 

```{r Forecast, eval = TRUE}
data(RV)
RV2 <- head(RV, 2001)
##Estimate/train tvHAR model
tvHAR <- with(RV2, tvAR (RV, p = 1, bw = 0.8, exogen = cbind(RV_week, RV_month)))
##Define the forecast horizon (n.ahead) and the future values of the exogenous variables
newexogen <- cbind(RV$RV_week[2002:2004], RV$RV_month[2002:2004])
##3-step-ahead forecast
forecast(tvHAR, n.ahead = 3, newexogen = newexogen)
```


The *forecast* method main arguments are *object* and *n.ahead*. The latter is a scalar with the forecast horizon. Depending on the class attribute, further arguments may be necessary.

###Type of forecast
It is possible to run either an increase window forecast (default), when argument *winsize = 0* or a rolling window forecast with a window size as long as it is defined in argument *winsize*.

###newdata
These are arguments in the *forecast* method containing the new values of the regressors and have class attributes *vector*, *data.frame* or *matrix*. It is not necessary to enter the intercept.

###newexogen
This argument appears in the *forecast* method for the class attributes *tvar* and *tvvar* and it must be entered when the initial model contains *exogen* variables. It is a *vector*, *data.frame* or *matrix*.


The *predict* method is implemented for the same four class attribues than the *forecast* method. It does not require the *n.ahead* or *winsize* arguments, but the other arguments are the same. In addition, new values of the smoothing variable must be entered into the argument *newz*. This is a *numeric* vector. The code below shows how to predict three future values of the *tvHARQ* model fitted above. The *tvHARQ* model has the same variables than the *tvHAR* model but the coefficients are unknown function of the past realized quarticity.

```{r Predict, eval = TRUE}
tvHARQ <- with(RV2, tvLM (RV ~ RV_lag + RV_week + RV_month, z = RQ_lag_sqrt, 
                bw = 0.003))
newdata <- cbind(RV$RV_lag[2002:2004], RV$RV_week[2002:2004], RV$RV_month[2002:2004])
newz <- RV$RQ_lag_sqrt[2002:2004]
predict(tvHARQ, newdata, newz)
```
 
The *predict* method for the rest of the class attributes in the package follow similar patterns and further examples can be found in the documentation of the package.


